---
title: "Assigment 1 RStudio Intro Class"
author: "Retsel Aimée González-Valentín"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: html_document
---
---

```{r setup, include=FALSE}
# Global chunk options. `include=FALSE` hides this setup chunk from the output.
knitr::opts_chunk$set(echo = TRUE)
```

## Q1. Assigning values

Create an object called `height` with the value 175 and print it.

```{r q1}
height <- 175
height          # print the object
```

## Q2. Simple math

Calculate the result of `25 * 4 - 10`.

```{r q2}
25 * 4 - 10     # multiplication happens before subtraction
```

## Q3. Using functions

Use the function `sqrt()` to calculate the square root of 81.

```{r q3}
sqrt(81)
```

## Q4. Character objects

Assign the phrase "R is fun!" to an object called `message` and print it.

```{r q4}
message <- "R is fun!"
message         # print the object
```

## Q5. Object manipulation

Create two objects `a <- 10` and `b <- 5`, then calculate their sum and store it in `c`.

```{r q5}
a <- 10
b <- 5
c <- a + b
c               # print the sum
```

## Q6. Logical comparison

Test whether 15 is greater than 20.

```{r q6}
15 > 20         # returns FALSE, because 15 is NOT greater than 20
```

## Q7. Checking classes

Check the class of the object `"Hello World"`.

```{r q7}
class("Hello World")   # returns "character"
```

## Q8. Code chunk options — suppress warnings

```{r q8, warning=FALSE}
log(-1)
```


## Q9. Code chunk options — suppress messages


```{r q9, message=FALSE}
# Load a package (may produce messages)
library(dplyr)
```


## Q10. Creating and analyzing a vector

Create a numeric vector called `grades`, calculate the average with
`mean()`, store it in `average`, and print the result.

```{r q10}
grades <- c(80, 90, 75, 95, 85)
average <- mean(grades)
average         # print the average (85)
```


